---
output: html_document
editor_options: 
  chunk_output_type: console
---
Top 200 novels in the United Kingdom according to https://en.wikipedia.org/wiki/The_Big_Read


```{r}
library(readr)
BBC <- read_csv("data/big-read-2.csv", col_names=c("place", "title", "author", "best list"))
```


DIE LESERWAHL DES ZDF: DAS GROSSE LESEN!
Quelle: 
https://www.dieterwunderlich.de/lesen_50.htm 
https://www.fabelhafte-buecher.de/buecher/die-wichtigsten-bucher-der-weltliteratur-aus-westlicher-sicht/die-leserwahl-des-zdf-das-grose-lesen/

```{r}
ZDF <- read_csv("data/big-read.csv", col_names=c("place", "title", "author", "best list"))
```


```{r}
leidos <- read_csv("data/leidos.csv")
```


The great american read
https://www.pbs.org/the-great-american-read/results/
Full Results
To Kill a Mockingbird
Outlander (Series)
Harry Potter (Series)
Pride and Prejudice
Lord of the Rings
Gone with the Wind
Charlotte's Web
Little Women
Chronicles of Narnia
Jane Eyre
Anne of Green Gables
Grapes of Wrath
A Tree Grows in Brooklyn
Book Thief
Great Gatsby
The Help
The Adventures of Tom Sawyer
1984
And Then There Were None
Atlas Shrugged
Wuthering Heights
Lonesome Dove
Pillars of the Earth
Stand
Rebecca
A Prayer for Owen Meany
Color Purple
Alice in Wonderland
Great Expectations
Catcher in the Rye
Where the Red Fern Grows
Outsiders
The Da Vinci Code
The Handmaid's Tale
Dune
The Little Prince
Call of the Wild
The Clan of the Cave Bear
The Hitchhiker's Guide to The Galaxy
The Hunger Games
The Count of Monte Cristo
The Joy Luck Club
Frankenstein
The Giver
Memoirs of a Geisha
Moby Dick
Catch 22
Game of Thrones (series)
Foundation (series)
War and Peace
Their Eyes Were Watching God
Jurassic Park
The Godfather
One Hundred Years of Solitude
The Picture of Dorian Gray
The Notebook
The Shack
A Confederacy of Dunces
The Hunt for Red October
Beloved
The Martian
The Wheel of Time (series)
Siddhartha
Crime and Punishment
The Sun Also Rises
The Curious Incident of the Dog in the Nighttime
A Separate Peace
Don Quixote
The Lovely Bones
The Alchemist
Hatchet (series)
Invisible Man
The Twilight Saga (series)
Tales of the City (series)
Gulliver's Travels
Ready Player One
Left Behind (series)
Gone Girl
Watchers
The Pilgrim's Progress
Alex Cross Mysteries (series)
Things Fall Apart
Heart of Darkness
Gilead
Flowers in the Attic
Fifty Shades of Grey
The Sirens of Titan
This Present Darkness
Americanah
Another Country
Bless Me, Ultima
Looking for Alaska
The Brief Wondrous Life of Oscar Wao
Swan Song
Mind Invaders
White Teeth
Ghost
The Coldest Winter Ever
The Intuitionist
Doña Bárbára