---
title: "List of research outputs"
author: "JR Ferrer-Paris"
date: "04/09/2022"
output: html_document
---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RefManageR)
BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear",
           bib.style = "authoryear",hyperlink = FALSE)
```


```{r,echo=FALSE}
bib1 <- ReadBib("bibTeX/peer-review.bibtex", check = FALSE)
bib2 <- ReadBib("bibTeX/preprints.bibtex", check = FALSE)
bib3 <- ReadBib("bibTeX/presentations.bibtex", check = FALSE)
bib4 <- ReadBib("bibTeX/reports.bibtex", check = FALSE)
bib5 <- ReadBib("bibTeX/datasets.bibtex", check = FALSE)
bib6 <- ReadBib("bibTeX/code-and-software.bibtex", check = FALSE)
NoCite(bib = bib1, 1:length(bib1), .opts = list(hyperlink = FALSE))
NoCite(bib = bib2, 1:length(bib2), .opts = list(hyperlink = FALSE))
NoCite(bib = bib3, 1:length(bib3), .opts = list(hyperlink = FALSE))
NoCite(bib = bib4, 1:length(bib4), .opts = list(hyperlink = FALSE))
NoCite(bib = bib5, 1:length(bib5), .opts = list(hyperlink = FALSE))
NoCite(bib = bib6, 1:length(bib6), .opts = list(hyperlink = FALSE))
```

This is where I keep my list of research outputs, from published research to datasets and reports. All this information comes from bibtex files in folder `bibTeX`. I use the package `RefManageR` to manage this information in a Rmarkdown document. This is an example of a single citation in the text with hyperlinks to the original document`r AutoCite(bib2, "Bland_Impact_RLE_preprint", .opts = list(hyperlink = "to.doc"))`. And this is another with multiple references and no hyperlinks `r AutoCite(bib5, publisher = "figshare", .opts = list(hyperlink = FALSE))`.


## Peer reviewed

This is the list of publication with peer-review, includes articles in journals and reports subjected to peer-review.

--- 

```{r results = "asis", echo = FALSE}
PrintBibliography(bib1, .opts = list(check.entries = FALSE, max.names=100, sorting = "ydnt"))
```

## Preprints

I added here references to some pre-prints, but most of them have been already published.

--- 

```{r results = "asis", echo = FALSE}
PrintBibliography(bib2, .opts = list(check.entries = FALSE,  max.names=100, sorting = "ydnt"))
```

## Presentations

These is a incomplete list of (mostly older) presentations in national or international events. Some of these presentations/posters are deposited in digital form in open source repositories with a DOI or another permanent identifier. 

--- 

```{r results = "asis", echo = FALSE}
PrintBibliography(bib3, .opts = list(check.entries = FALSE,  max.names=100, sorting = "ydnt"))
```

## Reports

These are reports that I produced and deposited in open source repositories, most of them have a DOI or another permanent identifier.

--- 

```{r results = "asis", echo = FALSE}
PrintBibliography(bib4, .opts = list(check.entries = FALSE,  max.names=100, sorting = "ydnt"))
```


## Datasets

> These are datasets that I have deposited in open source repositories, most of them have a DOI or another permanent identifier.

--- 

```{r results = "asis", echo = FALSE}
PrintBibliography(bib5, .opts = list(check.entries = FALSE,  max.names=100, sorting = "ydnt"))
```


## Code and software

> This is the list of code and software that I deposited in open source repositories, most of them have a DOI or another identifier.

--- 
```{r results = "asis", echo = FALSE}
PrintBibliography(bib6, .opts = list(check.entries = FALSE,  max.names=100, sorting = "ydnt"))
```