---
author: "José R. Ferrer Paris"
title: "This is how we built this!"
editor_options: 
  chunk_output_type: console
---

## No place like home

This is a test of a personal website for [jrfep](https://jrfep.github.io/)

All files are available in a [GitHub repository](https://github.com/jrfep/jrfep.github.io). The `mostly-harmless` branch uses Rmarkdown to build the site.

I am just [following](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html) [instructions](https://garrettgman.github.io/rmarkdown/rmarkdown_websites.html).


## Libraries

To manage and update the version of libraries that we need, we use `renv`:

We need to run different commands, until all the changes have been synchronised[^1] :

```{r eval=FALSE}
renv::init()
renv::status()
renv::install()
renv::status()
renv::snapshot()
```

## Render site

Run this (in RStudio) to render site locally:
```{r eval=FALSE}
rmarkdown::render_site()
```

Or preview one file
```{r eval=FALSE}
rmarkdown::render_site("presentations.Rmd")
```

Sing [All the rowboats](https://youtu.be/2CZ8ossU4pc) in the meantime (optional).

If this work, we can just `git push` it to the repo and see the changes!

## Alternatives

My [other branch](https://github.com/jrfep/jrfep.github.io/tree/jekyll) uses Jekyll (but I gave up on that some time ago, so do not expect any updates).

I [also tried](https://github.com/jrfep/jrfep.github.io/tree/mrhyde) Rmarkdown for some time, might get back to that if this one does not work. 

## Just in case

![ [Stand back, I know regular expressions.](https://xkcd.com/208/)](https://imgs.xkcd.com/comics/regular_expressions.png)


[^1]: Yes, I use this [weird spelling...](https://english.stackexchange.com/questions/230494/should-i-always-use-the-ised-ending-for-uk-english-and-the-ized-for-us)

## Flexdashboard and iNaturalist

Inspired by this example:
https://github.com/gonzalobravoargentina/inat_flexdashboard_ARG

### Get the data

I first install the `rinat` package:
```{r eval=FALSE}
here::i_am("README.Rmd")
if (!require(rinat)) {
  install.packages("rinat")
  library(rinat)
}
```

Then I can download the observations from iNaturalist and save them in a data folder:

```{r eval=FALSE}
# Download observations and save to RDS file
user_obs <- get_inat_obs_user("NeoMapas",maxresults = 5000)
if (!dir.exists(here::here("data")))
    dir.create(here::here("data"))
file_name <- here::here("data","iNaturalist-obs-NeoMapas.rds")
saveRDS(file=file_name, user_obs)

```

### Get a logo

With `wget` and ImageMagick, it is easy to download and resize in the terminal (`bash`) with two lines of code:

```sh
##mkdir 
wget https://neomapas.github.io/assets/images/logo_NeoMapas_p.gif
magick logo_NeoMapas_p.gif  -resize 100x148  resize_logo.gif
```

