---
author: "José R. Ferrer Paris"
title: "This is how we built this!"
editor_options: 
  chunk_output_type: console
---

## No place like home

This is a test of a personal website for [jrfep](https://jrfep.github.io/).

These instructions are in English, but this site has content in multiple languages... I know it is confusing, but this is how I work. If you require clarifications please open an issue or send me a message. 

All files are available in a [GitHub repository](https://github.com/jrfep/jrfep.github.io).  The `mostly-harmless` branch uses [Quarto](https://quarto.org/docs/websites/) to build the site.


## Libraries

To manage and update the version of libraries that we need, I used `renv` for some iterations, but it was complex to keep version across machines and different OSs...

When we use `renv` we need to run different commands, until all the changes have been synchronised[^1] :

```{r}
#| eval: false
renv::init()
renv::status()
renv::install()
renv::status()
renv::snapshot()
```

But if we don't update the .gitignore file things can get messy.

## Render site

With Rmarkdown we could run this (in RStudio) to render site locally:
```{r}
#| eval: false
rmarkdown::render_site()
```

Or preview one file
```{r}
#| eval: false
rmarkdown::render_site("presentations.Rmd")
```

With quarto and RStudio we can open the Build tab and select Build Website...

Or we can go to the command line and render the site: 

```{sh}
#| eval: false
quarto render 
```

Sing [All the rowboats](https://youtu.be/2CZ8ossU4pc) in the meantime (optional).

And then launch a preview:

```{sh}
#| eval: false
quarto preview
```

If this work, we can just `git add`, `git commit` and `git push` it to the repo and see the changes!

## Alternatives

My [other branch](https://github.com/jrfep/jrfep.github.io/tree/jekyll) uses Jekyll (but I gave up on that some time ago, so do not expect any updates).

I [also tried](https://github.com/jrfep/jrfep.github.io/tree/mrhyde) Rmarkdown for some time, might get back to that if this one does not work. 

I was tempted to create a multi-lingual site using [babelquarto](https://github.com/ropensci-review-tools/babelquarto):

```{r}
#| eval: false
install.packages('babelquarto', repos = c('https://ropensci.r-universe.dev', 'https://cloud.r-project.org'))
```

But it was a short-lived experiment. I think it could work for simple sites, but would require more tweaks to make it work with my current site. 

## Font Awesome

They work well out of the box with Rmarkdown, but for quarto we need to install an extension.

Switch to the repository folder and checkout the git branch we are working on, and then:

```sh
quarto install extension quarto-ext/fontawesome
```

Now I can use `{{{< fa smile >}}}` in the text and get a {{< fa smile >}}, or `{{{< fa lemon >}}}` and get a {{< fa lemon >}}.

## Just in case

![ [Stand back, I know regular expressions.](https://xkcd.com/208/)](https://imgs.xkcd.com/comics/regular_expressions.png)


[^1]: Yes, I use this [weird spelling...](https://english.stackexchange.com/questions/230494/should-i-always-use-the-ised-ending-for-uk-english-and-the-ized-for-us)

## Prepare data for some pages

### OSF data

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
if (!require(osfr)) {
  install.packages("osfr")
  library(osfr)
}
lst_osf <- osf_retrieve_user("me") %>%
  osf_ls_nodes()
if (!dir.exists(here::here("data")))
    dir.create(here::here("data"))
file_name <- here::here("data","OSF-data.rds")
saveRDS(file=file_name, lst_osf)
```


### GitHub data

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
if (!require(jsonlite)) {
  install.packages("jsonlite")
  library(jsonlite)
}
gh_rle_org <- read_json("https://api.github.com/orgs/red-list-ecosystem/repos")
gh_ces_org <- read_json("https://api.github.com/orgs/ces-unsw-edu-au/repos")
gh_jrfep <- read_json("https://api.github.com/users/jrfep/repos")
# https://api.github.com/search/repositories?q=user:jrfep&fork:false
# for each repo query the languages_url and summarise the lines of code for each language
file_name <- here::here("data","GitHub-data.rda")
save(file=file_name, gh_rle_org, gh_ces_org, gh_jrfep)
```

### Flexdashboard and iNaturalist

I use to have a dashboard here, but it works better with Rmarkdown than with quarto. SO I moved it to another site/repo.

There might be some alternatives in quarto for this, but haven't tested them yet.

That OLD dashboard was inspired by this example:
https://github.com/gonzalobravoargentina/inat_flexdashboard_ARG

To get the data I first install the `rinat` package:

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
if (!require(rinat)) {
  install.packages("rinat")
  library(rinat)
}
```

Then I can download the observations from iNaturalist and save them in a data folder:

```{r}
#| eval: false
# Download observations and save to RDS file
user_obs <- get_inat_obs_user("NeoMapas",maxresults = 5000)
if (!dir.exists(here::here("data")))
    dir.create(here::here("data"))
file_name <- here::here("data","iNaturalist-obs-NeoMapas.rds")
saveRDS(file=file_name, user_obs)

```

To get the logo

With `wget` and ImageMagick, it is easy to download and resize in the terminal (`bash`) with two lines of code:

```sh
##mkdir 
wget https://neomapas.github.io/assets/images/logo_NeoMapas_p.gif
magick logo_NeoMapas_p.gif  -resize 100x148  resize_logo.gif
```

### Photos from Flickr

So, I think I need some photos in my website, and I have a Flickr account, and I use R, there should be a library that...

Oh yes! found it!

<https://koki25ando.github.io/FlickrAPI/>

```{r}
#| eval: false
install.packages("FlickrAPI")
```

Now I need a [Flickr API key](https://www.flickr.com/services/developer/) 

```{r}
#| eval: false
library(FlickrAPI)
setFlickrAPIKey(api_key = "YOUR_API_KEY_HERE", install = TRUE)
```

And finally, it works!

Let's now query our photos (up to 1000) and save the information in a RDS file:

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
library(FlickrAPI)
library(foreach)
library(dplyr)
readRenviron("~/.Renviron") # read the API key
here::i_am("how2/how-to-site.qmd")
photos <- foreach(u=c("jferrer","jferrer","199798864@N08"), i=c(1,2,1),.combine = "bind_rows") %do% {
  getPhotos(user_id = u, img_size="m", extras = c("description","owner_name",
  "url_m"), per_page=1000, page=i)
}

dim(photos)

file_name <- here::here("data","flickr-photos.rds")
saveRDS(file=file_name, photos)
```

### Photos from google 

This is a trial-and-error test of reading my photos from a google account, based on [some blogs](https://www.listendata.com/2021/10/r-wrapper-for-google-photos-api.html), [medium posts](https://max-coding.medium.com/loading-photos-and-metadata-using-google-photos-api-with-python-7fb5bd8886ef) and [stack overflow posts](https://stackoverflow.com/questions/50573196/access-google-photo-api-with-python-using-google-api-python-client):

1. I created a project in google cloud, 
2. enabled Photos Library API (not sure if this is relevant here),
3. configured a simple consent page, 
4. created a OAuth 2.0 client ID and downloaded the json file.
5. added `GC_PROJECT_EMAIL` and `GC_PROJECT_CRED_JSON` to my .Renviron file

Then I ran these lines of code

```{r}
#| eval: false
library(gargle)
library(dplyr)
library(jsonlite)
library(httr)

readRenviron("~/.Renviron")
cred_json <- Sys.getenv("GC_PROJECT_CRED_JSON")
if (!file.exists(cred_json)) {
  stop("credentials not found, please update Renviron file")
} else {
  clnt <- gargle_oauth_client_from_json(path=cred_json)
}

tkn <- gargle2.0_token(
  email = Sys.getenv("GC_PROJECT_EMAIL"),
  client = clnt,
  scope = c("https://www.googleapis.com/auth/photoslibrary.readonly", # need to remove the "readonly"
            "https://www.googleapis.com/auth/photoslibrary.sharing")
)
k <- token_fetch(token=tkn)
authorization = paste('Bearer', k$credentials$access_token)

getalbum <-
  GET("https://photoslibrary.googleapis.com/v1/albums",
      add_headers(
        'Authorization' = authorization,
        'Accept'  = 'application/json')) %>% 
  content(., as = "text", encoding = "UTF-8") %>%
  fromJSON(., flatten = TRUE) %>% 
  data.frame()

aID <- getalbum %>% filter(albums.title %in% "Tesaurus") %>% pull(albums.id)

photos <-
  POST("https://photoslibrary.googleapis.com/v1/mediaItems:search",
    add_headers(
      'Authorization' = authorization,
      'Accept'  = 'application/json'),
    body = list("albumId" = aID,
                "pageSize" = 25),
    encode = "json"
    ) %>% 
  content(., as = "text", encoding = "UTF-8") %>%
  fromJSON(., flatten = TRUE) %>% 
  data.frame()

here::i_am("how2/how-to-site.qmd")
file_name <- here::here("data","google-photos.rds")
saveRDS(file=file_name, photos)
```

This downloads the information, but it does not allow to share the links to the photos (they become defunct after the session is closed). It seems that the way forward would be to select existing files, [create shareable albums with the API](https://developers.google.com/photos/library/guides/share-media#rest) and download the shareableURL of the album and photos. Still needs some testing...

### Galleries with `pixture`

I am experimenting with the [pixture package](https://www.royfrancis.com/pixture/index.html) to create image galleries.

```{r}
#| eval: false
install.packages(c("htmlwidgets","shiny","remotes"))
remotes::install_github('royfrancis/pixture')
```